Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Paris version \YellowPaperVersionNumber}}

### 2024-01-10 Paper.tex
grammar edits

After reaching the \textit{terminal block} described in section \ref{ch:pos_transition}, the greatest \textit{total difficulty} rule must be removed in favor of a rule known as \textit{LMD Ghost}\footnote{\textit{LMD GHOST} comprises two acronyms, "Latest Message Driven", and "Greedy Heaviest-Observed Sub-Tree".}.

Note that in order to determine what blocks comprise the canonical Ethereum blockchain after \textit{Paris}, one must have additional information from the beacon chain, which is not described herein. We denote events emitted by the beacon chain with the prefix $\mathtt{POS\_}$.

>>>>

After reaching the \textit{terminal block} described in section \ref{ch:pos_transition}, the greatest \textit{total difficulty} rule must be removed in favor of a rule known as \textit{LMD Ghost}.\footnote{\textit{LMD GHOST} comprises two acronyms, "Latest Message Driven", and "Greedy Heaviest-Observed Sub-Tree".}

Note that in order to determine what blocks comprise the canonical Ethereum blockchain after \textit{Paris}, one must have additional information from the Beacon Chain, which is not described herein. We denote events emitted by the Beacon Chain with the prefix $\mathtt{POS\_}$.
